Resting energy expenditure of women with and without polycystic ovary syndrome: a systematic review and meta-analysis\thanks{Corresponding author: James Steele (Email: james@steele-research.com; ORCID: 0000-0002-8003-0757)}

### 2025-12-03 manuscript/pre_print.qmd
Add contributions to preprint and submission

>>>>

# Contributions
Gregory Nuckols and Leigh Peele conceived the idea for the project. All authors contributed to the design of the project and methods. Richie Kirwan and Leigh Peele conducted the systematic search and screening. James Steele performed the data extraction, conducted the statistical analyses, and produced the data visualisations. All authors contributed to drafting the initial manuscript. All authors contributed to editing the manuscript. All authors read and approved the final manuscript.

### 2025-12-03 manuscript/pre_print.tex
Add contributions to preprint and submission

>>>>

\section{Contributions}\label{contributions}

Gregory Nuckols and Leigh Peele conceived the idea for the project. All
authors contributed to the design of the project and methods. Richie
Kirwan and Leigh Peele conducted the systematic search and screening.
James Steele performed the data extraction, conducted the statistical
analyses, and produced the data visualisations. All authors contributed
to drafting the initial manuscript. All authors contributed to editing
the manuscript. All authors read and approved the final manuscript.

### 2025-12-03 manuscript/submission_manuscript.qmd
Add contributions to preprint and submission

---
title: |
  Resting energy expenditure of women with and without polycystic ovary syndrome: a systematic review and meta-analysis
date: last-modified
date-format: long
format:
  pdf:
    # documentclass: article
    keep-tex: true
    template-partials: 
     - title.tex
    pdf-engine: xelatex
    mainfont: "Latin Modern Roman"
    include-in-header:
      text: |
        \usepackage{lineno}\linenumbers
        \usepackage{setspace}\AtBeginDocument{\spacing{2}}
        \usepackage[font=scriptsize]{caption}
        \usepackage{pdflscape}
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
        \usepackage{etoolbox}
geometry:
  - left=1in
  - right=1in
  - top=1in
  - bottom=1in
author:
  - name: Richard Kirwan
    affil-id: 1
    orcid: 0000-0003-4645-0077
    email: R.P.Kirwan@ljmu.ac.uk
  - name: Leigh Peele
    affil-id: 2
    email: leigh@macrofactorapp.com
  - name: Gregory Nuckols
    affil-id: 2
    orcid: 0009-0004-2679-7967
    email: greg@macrofactorapp.com
  - name: Georgia Kohlhoff
    affil-id: 3
    email: g_kohlhoff@hotmail.co.uk
  - name: Hannah Cabré
    affil-id: 4
    orcid: 0000-0002-3235-6867
    email: Hannah.Cabre@pbrc.edu
  - name: Alyssa Olenick
    affil-id: 5
    orcid: 0000-0002-2217-8067
    email: alyssaolenickphd@gmail.com
  - name: James Steele
    affil-id: 2,6,7
    orcid: 0000-0002-8003-0757
    corresponding: true
    email: james@steele-research.com
affiliations:
  - id: 1
    name: Research Institute for Sports and Exercise Sciences, Liverpool John Moores University, Liverpool, UK
  - id: 2
    name: MacroFactor, Stronger by Science Technologies LLC, Raleigh, North Carolina, USA
  - id: 3
    name: Flourishing Health, Liverpool, UK
  - id: 4
    name: Reproductive Endocrinology and Women’s Health Research Program, Pennington Biomedical Research Center, Baton Rouge, Louisiana, USA
  - id: 5
    name: Dr Alyssa Olenick LLC
  - id: 6
    name: Steele Research Limited, Eastleigh, Hampshire, UK
  - id: 7
    name: School of Health and Biomedical Sciences, Royal Melbourne Institute of Technology, Melbourne, VIC, Australia
thanks: |
  Corresponding author: James Steele (james@steele-research.com)
bibliography: 
  mylibrary.bib
csl: american-medical-association.csl
execute: 
  echo: false
  message: false
  warning: false
---
```{r}
library(tidyverse)
library(flextable)
library(tidybayes)

>>>>

---
title: |
  Resting energy expenditure of women with and without polycystic ovary syndrome: a systematic review and meta-analysis
date: last-modified
date-format: long
format:
  pdf:
    # documentclass: article
    keep-tex: true
    template-partials: 
     - title.tex
    pdf-engine: xelatex
    mainfont: "Latin Modern Roman"
    include-in-header:
      text: |
        \usepackage{lineno}\linenumbers
        \usepackage{setspace}\AtBeginDocument{\spacing{2}}
        \usepackage[font=scriptsize]{caption}
        \usepackage{pdflscape}
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
        \usepackage{etoolbox}
geometry:
  - left=1in
  - right=1in
  - top=1in
  - bottom=1in
author:
  - name: Richard Kirwan
    affil-id: 1
    orcid: 0000-0003-4645-0077
    email: R.P.Kirwan@ljmu.ac.uk
  - name: Leigh Peele
    affil-id: 2
    email: leigh@macrofactorapp.com
  - name: Gregory Nuckols
    affil-id: 2
    orcid: 0009-0004-2679-7967
    email: greg@macrofactorapp.com
  - name: Georgia Kohlhoff
    affil-id: 3
    email: g_kohlhoff@hotmail.co.uk
  - name: Hannah Cabré
    affil-id: 4
    orcid: 0000-0002-3235-6867
    email: Hannah.Cabre@pbrc.edu
  - name: Alyssa Olenick
    affil-id: 5
    orcid: 0000-0002-2217-8067
    email: alyssaolenickphd@gmail.com
  - name: James Steele
    affil-id: 2,6,7
    orcid: 0000-0002-8003-0757
    corresponding: true
    email: james@steele-research.com
affiliations:
  - id: 1
    name: Research Institute for Sports and Exercise Sciences, Liverpool John Moores University, Liverpool, UK
  - id: 2
    name: MacroFactor, Stronger by Science Technologies LLC, Raleigh, North Carolina, USA
  - id: 3
    name: Flourishing Health, Liverpool, UK
  - id: 4
    name: Reproductive Endocrinology and Women’s Health Research Program, Pennington Biomedical Research Center, Baton Rouge, Louisiana, USA
  - id: 5
    name: Dr Alyssa Olenick LLC
  - id: 6
    name: Steele Research Limited, Eastleigh, Hampshire, UK
  - id: 7
    name: School of Health and Biomedical Sciences, Royal Melbourne Institute of Technology, Melbourne, VIC, Australia
thanks: |
  Corresponding author: James Steele (Email: james@steele-research.com; ORCID: 0000-0002-8003-0757)
bibliography: 
  mylibrary.bib
csl: american-medical-association.csl
execute: 
  echo: false
  message: false
  warning: false
---
```{r}
library(tidyverse)
library(flextable)
library(tidybayes)

### 2025-12-03 manuscript/submission_manuscript.tex
Add contributions to preprint and submission

\title{Resting energy expenditure of women with and without polycystic
ovary syndrome: a systematic review and
meta-analysis\thanks{Corresponding author: James Steele
(james@steele-research.com)}}

>>>>

\title{Resting energy expenditure of women with and without polycystic
ovary syndrome: a systematic review and
meta-analysis\thanks{Corresponding author: James Steele (Email:
james@steele-research.com; ORCID: 0000-0002-8003-0757)}}
